Missing the Point: Non-Convergence in Iterative Imputation Algorithms

### 2020-05-11 3.Thesis/Writeup/2.Manuscript.tex
Now with correct layout

\hypertarget{summary.-overall-the-methods-to-diagnose-non-convergence-perform-as-expected-they-indicate-more-signs-of-non-convergence-in-conditions-with-worse-performance-in-terms-of-bias-and-confidence-validity.-under-low-to-moderate-missingness-it-does-not-seem-to-matter-on-which-theta-the-non-convergence-diagnostics-are-applied.-if-we-look-at-complete-unbiasedness-however-we-notice-that-univariate-thetas-fail-to-diagnose-the-persistent-bias-in-conditions-where-p_rm-incgeq.75.}{%
\subsubsection{\texorpdfstring{Summary. Overall, the methods to diagnose non-convergence perform as expected: they indicate more signs of non-convergence in conditions with worse performance in terms of bias and confidence-validity. Under low to moderate missingness, it does not seem to matter on which \(\theta\) the non-convergence diagnostics are applied. If we look at complete unbiasedness, however, we notice that univariate \(\theta\)s fail to diagnose the persistent bias in conditions where \(p_{\rm inc}\geq.75\).}{Summary. Overall, the methods to diagnose non-convergence perform as expected: they indicate more signs of non-convergence in conditions with worse performance in terms of bias and confidence-validity. Under low to moderate missingness, it does not seem to matter on which \textbackslash theta the non-convergence diagnostics are applied. If we look at complete unbiasedness, however, we notice that univariate \textbackslash thetas fail to diagnose the persistent bias in conditions where p\_\{\textbackslash rm inc\}\textbackslash geq.75.}}\label{summary.-overall-the-methods-to-diagnose-non-convergence-perform-as-expected-they-indicate-more-signs-of-non-convergence-in-conditions-with-worse-performance-in-terms-of-bias-and-confidence-validity.-under-low-to-moderate-missingness-it-does-not-seem-to-matter-on-which-theta-the-non-convergence-diagnostics-are-applied.-if-we-look-at-complete-unbiasedness-however-we-notice-that-univariate-thetas-fail-to-diagnose-the-persistent-bias-in-conditions-where-p_rm-incgeq.75.}}

>>>>

\hypertarget{summary.-1}{%
\subsubsection{Summary.}\label{summary.-1}}

Overall, the methods to diagnose non-convergence perform as expected: they indicate more signs of non-convergence in conditions with worse performance in terms of bias and confidence-validity. Under low to moderate missingness, it does not seem to matter on which \(\theta\) the non-convergence diagnostics are applied. If we look at complete unbiasedness, however, we notice that univariate \(\theta\)s fail to diagnose the persistent bias in conditions where \(p_{\rm inc}\geq.75\).
